A new tidy data structure to support exploration and modeling of temporal data

### 2019-08-25 reviews/response.Rmd

We thank the reviewers for their helpful feedback which has led to many improvements in the paper. The point by point description of changes are below: the reviewers' comments are in red and our response is in black.

This manuscript has undergone an overhaul to address reviewer's comments:

1. Section 2.2 (previously 2.3) reviews existing time series and longitudinal data standards in popular statistical software, such as R, Stata, and SAS.
2. We have rewritten Section 3 "Contextual semantics" to give a definition of tsibble in relation to tidy data, and we expand on the four rules of a tsibble in details.
3. We have rewritten Section 4 "Temporal data pipelines" to describe a big picture about each module with the focus of temporal data instead of time series before. We have added Section 4.4 to summarise what a fluent pipeline looks like for a tsibble.
4. We have removed the mosaic plot along with the paragraph from Section 6.1, and added the forecasting example to the smart meter data in Section 6.2 to show tsibble's capability.

Along with these major changes, we have done lots of minor tweaks to improve the manuscript.

@@

# Reviewer 1 comments {-}

> More mini examples embeded throughout the manuscript. Mainly it didn't showcase to me tsibble's capability well enough but understandably this may make the manuscript long and may be better left to vignettes.

We have added a code snippet (featuring new `pedestrian` dataset) in a new subsection 4.4, and the load forecasting example to the energy consumption case study to show the cleaner, more expressive temporal data pipeline.

@@

> Figure 11 with missing data was a great demonstration for tsibble and the data times series pipeline shown in Figure 3. It may be helpful to reduce the opacity of the points as there is a lot of overplotting. The top line which lumps a number of customers together is not particularly informative here. Perhaps it is better replaced with a histogram.

TODO.

> Authors may like to add/change `spread`/`gather` verbs to `pivot_longer`/`pivot_wider` with the recent move to deprecate the former in tidyr. Likewise authors may like to consider to replace “long data” to “longer data” and “wide data” to “wider data” as long/wide implies absolute terms. <https://tidyr.tidyverse.org/dev/articles/pivot.html>

We'd like to upgrade `spread`/`gather` verbs to `pivot_longer`/`pivot_wider`. But they are not S3 generics yet, which delays the implementation. Conceptually the newly melt columns will be added to the key specification.

@@

> Manuscript does implicitly feel more time series data oriented rather than a general temporal data. E.g. references of time points as index seems inherent from other time series data infrastructure (i.e. zoo and xts) and the presented case studies is not representative of any longitudinal study. This does not mean it should be changed but index to me was not as intuitive to be the temporal variable.

[TODO]

Time indexes lay the contextual foundation to both time series and longitudinal data. `zoo` and `xts` store indices as metadata due the matrix structure, but tsibble's indices are explicitly a data column that can be manipulated. Tsibble also has the capacity of custom index support and interval extraction.

Tsibble is aimed at general temporal data, to unify time series and longitudinal **data**. In the revised manuscript (Section 4), we note the focuses of time series and longitudinal **analysis** are different in the modelling practice. Yes, the presented case studies are time series oriented, because currently time series model functions are available for tsibble.

### 2019-08-25 tsibble.Rmd
updated response

```{r external, include = FALSE, cache = FALSE}
read_chunk('scripts/demo.R')
read_chunk('scripts/flights.R')
read_chunk('scripts/smart-meter.R')
ggplot2::theme_set(ggplot2::theme_bw())
```

>>>>

```{r external, include = FALSE, cache = FALSE}
read_chunk('scripts/demo.R')
read_chunk('scripts/flights.R')
read_chunk('scripts/smart-meter.R')
```
